### 2014-04-14 paper_skeleton.tex
reorganizing code

@@

@@

The outcome of the decision process is not deterministic. Because of the noise in this system, the utility of a decision depends on the probability of reaching the correct decision and the expected time it takes to reach a decision.  These quantities satisfy partial differential equations with respect to the starting values of the decision variables. In Appendix \ref{pdes_deriv}, we derive these partial differential equations.  While an analytical solution is known in the one-dimensional case, the two-dimensional case is analytically intractable.  We therefore numerically solve the PDEs in the two-dimensional case.

@@

@@

>>>>

%note about applicability to quorum sensing?!?

@@

Each decision variable, $X_1$ and $X_2$, accumulates information about the stimulus.  The sign and size of the two variables indicate how much evidence there is for each possible decision outcome.  When a lot of evidence for the first possibility has been observed, $X_1$ will be large and positive, and similarly for the second possibility.  If the difference in the variables can be observed, the difference indicates the relative strengths of the evidence for either possibility. If $Y=X_1-X_2$, when $Y$ is large enough the system decides on $X_1$ and when $Y$ is low enough the system decides on $X_2$.  Specifically, there are two thresholds, $-T_2$ and $T_1$ such that if $Y<-T_2$ the decision is for $X_2$ and if $Y>T_1$ the decision is for $X_1$.  However, it may be the case that the difference in the variables cannot be observed.  In this case, the decision depends on whether $X_1$ or $X_2$ hits a threshold first.  Again, there are two thresholds, now $-T_2$ and $-T_1$ and if $X_1<-T_1$ the decision is for $X_1$ and if the $X_2<-T_2$ the decision is for $X_2$.

In either case, the thresholds affect the expected time until a decision is reached (decision time, DT), the probability that an incorrect decision is made (error rate, ER), and, in the social case, the probability for each animal that he will emit a subordination signal (signaling probability, $\text{SP}_i$).  These quantities, DT, ER, and $\text{SP}_i$, satisfy partial differential equations with respect to the starting values of the decision variables. In Appendix \ref{pdes_deriv}, we derive these partial differential equations.  While an analytical solution is known in the one-dimensional case, the two-dimensional case is analytically intractable.  We therefore numerically solve the PDEs in the two-dimensional case.

@@

@@

When waiting for a decision to be made is more costly, so that minimizing DT is prioritized, the resulting distribution of the number of signals received is more skewed with a heavier right tail (Figure \ref{skewness}).

@@

\begin{figure}

\caption{\label{givingup} }
\end{figure}

\begin{figure}

\caption{\label{skewness} }
\end{figure}
